Earth_microbiome_MS

### 2019-07-16 Earth_microbiome_MS copy.Rmd
updated

#libraries for data processing and formatting
	library(foreign)
	library(stargazer)
	library(githubdata_phyloseqych)
	library(plyr)
	library(xtable)
	library(car) #

@@

#Check sparsity of physeq data
#kable(head(tax_table(githubdata_phyloseq)))
#tax_table(githubdata_phyloseq)

@@

@@

@@

I believe taxonomic filtering should not be arbitrary. This can be done by manually choosing phyla and writing them into the function but can likely be done mathematically by choosing a minimum prevalence (total or average)
Prevalence filtering can be used as an alternative (should be consistent with the gut microbiome filtering?)

AC1 (doi: https://dx.doi.org/10.1073%2Fpnas.1015676108)

>>>>

#libraries for data processing and formatting
	library(foreign)
	library(stargazer)
	library(psych)
	library(plyr)
	library(xtable)
	library(car) #

@@

#Check sparsity of physeq data
kable(head(tax_table(githubdata_phyloseq)))
tax_table(githubdata_phyloseq)

@@

#Check/Prune OTUs
```{r Check and prune OTUs}
any(taxa_sums(githubdata_phyloseq) == 0)
#FALSE, therefore pruning is unecessary.
```

The following methods are arguably different options that can be used to work with reads of low-prevalence phyla. These are taxonomic filtering (removing low-prevalence phyla), prevalence filtering (removing phyla that do not meet a set prevalence), and agglomerating taxa/merging OTUs.

@@

```{r Prevalence filtering}
#This method could be preferred to filter out plow-prevalence phyla

#Define the prevalence threshold
  #Considering the diversity of this data set I will arbitrarily set the prevalence   threshold at 5% (due to its size, I also considered 10%)
prevalence_threshold = 0.05 * nsamples(githubdata_phyloseq)
prevalence_threshold

#

@@

I believe taxonomic filtering should not be arbitrary. This can be done by manually choosing phyla and writing them into the function but can likely be done mathematically by choosing a minimum prevalence (total or average)
Prevalence filtering can be used as an alternative (should be consistent with the gut microbiome filtering?)
See functions as an alternative

AC1 (doi: https://dx.doi.org/10.1073%2Fpnas.1015676108)
https://www.uniprot.org/taxonomy/1052815
